\documentclass[9pt,pdftex]{beamer}
\setbeamertemplate{section in toc}[sections numbered]
\setbeamertemplate{subsection in toc}%
{\leavevmode\leftskip=3em\rlap{\hskip-2em\inserttocsectionnumber.\inserttocsubsectionnumber}\inserttocsubsection\par}
% use git: import repository as new project in eclipse: http://www.eclipse.org/forums/index.php/t/226301/
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage[bf,small, format=plain]{caption}
\usepackage{color}

%\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{tikz,tikzscale,pgfplots,grffile}
\usetikzlibrary{arrows,shapes,backgrounds}
\usetikzlibrary{plotmarks}
\usepackage{bbding}

\usepackage[clock]{ifsym}

\usepackage{pgfplots}
\usepackage{grffile}
\pgfplotsset{compat=newest}

%\author{}
%\title{}
%\setbeamercovered{transparent} 
%\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
%\date{} 
%\subject{} 

\pgfdeclarelayer{bg}
\pgfsetlayers{bg,main}

\usepackage{listings}
\lstset{language=C++,
				breaklines=true,
				tabsize=8,
				showtabs=true,
                basicstyle=\ttfamily,
                keywordstyle=\color{blue}\ttfamily,
                stringstyle=\color{red}\ttfamily,
                commentstyle=\color{green}\ttfamily,
                morecomment=[l][\color{magenta}]{\#}
}
\usepackage{mdframed}
\usepackage{multicol}
\usepackage{tcolorbox}
%\usepackage{multirow}
% \usepackage{paralist}
%\usepackage[colorinlistoftodos]{todonotes}
%\usepackage{biblatex}
%usepackage[nolist,nohyperlinks]{acronym}
%\usepackage{amstext}
%\usepackage{hyperref} 
%\usepackage{comment}
%\usepackage{subcaption}
%\renewcommand*{\figureautorefname}{fig.}
%\renewcommand*{\equationautorefname}{eq.}
\usepackage{bm}
\usepackage{comment}
%\usepackage{beamerthemeshadow}
%\usepackage{tikz}
%\usepackage{pgfplots}
%\usepackage{ulem}
%\usepackage[lofdepth,lotdepth]{subfig}
%\newenvironment{figure*}%
%{\begin{figure}}
%{\end{figure}}
%\usepackage[style=mla,babel=hyphen,backend=biber]{biblatex}
% CSE-Beamer-Styles:
\usepackage[course]{beamertheme_sccstalk}
%\usepackage[lecture]{beamertheme_sccstalk}
\usepackage{beamercolorscheme_sccs}
\usepackage{beamerfontthemestructurebold}
\setcounter{tocdepth}{3} 
%colored blocks, example \begin{variableblock}{Title}{bg=blue,fg=white}{bg=white,fg=black}
\newenvironment{variableblock}[4]{%
\setbeamercolor{block title}{#2}
\setbeamercolor{block body}{#3}
\begin{block}{#1}\begin{mdframed}{#4}\end{mdframed}\end{block}}


%some useful commands
%\newcommand{\der}[2]{\frac{\text{d}#1}{\text{d}#2}}
\title{Assignment 3: MPI Point-to-Point and One-Sided Communication}
\subtitle{Programming of Super Computers}
\author[Friedrich Menhorn, Benjamin Rüth, Erik Wannerberg] {Friedrich Menhorn, Benjamin Rüth, Erik Wannerberg \\ Team 12} %[displayed in footer]{displayed on title page}
\date{\today}
\institute{Technische Universität München}
\newtheorem*{rem}{Remark}

\begin{document}
\frame{\maketitle}

\begin{frame}{Contents}
\tableofcontents
\end{frame}

\section{Provided Implementation and Baseline}
\begin{frame}{\phantom{Contents}}
\tableofcontents[
  currentsection  
]
\end{frame}

\subsection{Cannon’s algorithm}
\begin{frame}{\insertsubsection}
\begin{itemize}
\item explain algorithm
\item provided implementation
\end{itemize}
\end{frame}


\subsection{Baseline}
\begin{frame}{\insertsubsection}
Challenges in getting an accurate baseline and changes to the Load-Leveler batch script.
\end{frame}

\subsection{Scalability}
\begin{frame}{\insertsubsection}
\begin{itemize}
\item Compute time scalability with fixed 64 processes and varying size of input files.
\item MPI time scalability with fixed 64 processes and varying size of input files.
\item Differences in scalability between the Sandy Bridge and Haswell architectures.
\end{itemize}
\end{frame}

\section{MPI Point-to-Point Communication}
\begin{frame}{\phantom{Contents}}
\tableofcontents[
  currentsection  
]
\end{frame}
\subsection{MPI Non-Blocking Operations}
\begin{frame}{\insertsubsection}
\begin{itemize}
	\item Send/Receive
	\begin{itemize}
	\item \lstinline[basicstyle=\scriptsize\bf]{MPI_Isend}
	\item \lstinline[basicstyle=\scriptsize\bf]{MPI_Irecv}
	\end{itemize}

	\item Synchronization
	\begin{itemize}
	\item \lstinline[basicstyle=\scriptsize\bf]{MPI_Wait}
	\item \lstinline[basicstyle=\scriptsize]{MPI_Probe}
	\end{itemize}
	
\end{itemize}
\end{frame}
\subsection{Optimizations}
\begin{frame}{\insertsubsection}
\begin{itemize}
\item \textbf{What is overlap?}\\
	We do not wait for either task to be completed, but try to do communication and computation at the same time. We are hiding communication time by doing computation in the meantime.
\item \textbf{What is the theoretical maximum overlap that can be achieved?}\\
Bounds for pure communication time: $$\max\left(0, T_\text{MPI}^\text{blocking} - T_\text{computation}\right) \leq T_\text{MPI}^\text{non-blocking} \leq T_\text{MPI}^\text{blocking}$$
Overheads:
\begin{itemize}
\item Copying into and from buffers
\item Initialization
\end{itemize}
Maximum overlap depends on amount of $T_\text{computation}$. As soon as $T_\text{computation}>T_\text{MPI}^\text{blocking}$, we can theoretically achieve 100\% overlap.

\end{itemize}

\end{frame}

\begin{frame}{\insertsubsection \ (cond.)}
\begin{itemize}
\item \textbf{Was communication and computation overlap achieved?}
\end{itemize}
\end{frame}

\subsection{Scaling}
\begin{frame}{\insertsubsection}
\begin{itemize}
\item Was a speedup observed versus the baseline?
\item Were there any differences between Sandy Bridge and Haswell nodes?
\end{itemize}
\end{frame}

\section{MPI One-Sided Communication}
\begin{frame}{\phantom{Contents}}
\tableofcontents[
  currentsection  
]
\end{frame}
\subsection{MPI One-Sided Operations}
\begin{frame}{\insertsubsection}
\begin{itemize}
	\item Initialization
	\begin{itemize}
		\item \lstinline[basicstyle=\scriptsize\bf]{MPI_Win_create}
		\item \lstinline[basicstyle=\scriptsize\bf]{MPI_Win_free}
	\end{itemize}
	
	\item Remote Memory Access
	\begin{itemize}
		\item \lstinline[basicstyle=\scriptsize\bf]{MPI_Put}
		\item \lstinline[basicstyle=\scriptsize]{MPI_Get}
		\item \lstinline[basicstyle=\scriptsize]{MPI_Accumulate}                 
	\end{itemize}

	\item Synchronization
	\begin{itemize}
		\item \lstinline[basicstyle=\scriptsize\bf]{MPI_Win_fence}
		\item \lstinline[basicstyle=\scriptsize]{MPI_Win_post  /  MPI_Win_start /  MPI_Win_complete  / MPI_Win_wait}
		\item \lstinline[basicstyle=\scriptsize]{MPI_Win_lock / MPI_Win_unlock}
	\end{itemize}
\end{itemize}
\end{frame}


\subsection{Optimizations}
\begin{frame}{\insertsubsection}
\begin{itemize}
\item Was communication and computation overlap achieved?
\end{itemize}
\end{frame}

\subsection{Scaling}
\begin{frame}{\insertsubsection}
\begin{itemize}
\item Was a speedup observed versus the baseline?
\item Was a speedup observed versus the non-blocking version?
\item Were there any differences between Sandy Bridge and Haswell nodes?
\end{itemize}
\end{frame}

\end{document}
