\documentclass[9pt,pdftex]{beamer}
\setbeamertemplate{section in toc}[sections numbered]
\setbeamertemplate{subsection in toc}%
{\leavevmode\leftskip=3em\rlap{\hskip-2em\inserttocsectionnumber.\inserttocsubsectionnumber}\inserttocsubsection\par}
% use git: import repository as new project in eclipse: http://www.eclipse.org/forums/index.php/t/226301/
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsfonts, amsmath, amssymb}
\usepackage[bf,small, format=plain]{caption}
\usepackage{color}

%\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{tikz,tikzscale,pgfplots,grffile}
\usetikzlibrary{arrows,shapes,backgrounds}
\usetikzlibrary{plotmarks}
\usepackage{bbding}

\usepackage[clock]{ifsym}

\usepackage{pgfplots}
\usepackage{grffile}
\pgfplotsset{compat=newest}

%\author{}
%\title{}
%\setbeamercovered{transparent} 
%\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
%\date{} 
%\subject{} 

\pgfdeclarelayer{bg}
\pgfsetlayers{bg,main}

\usepackage{listings}
\lstset{language=C++,
				breaklines=true,
				tabsize=8,
				showtabs=true,
                basicstyle=\ttfamily,
                keywordstyle=\color{blue}\ttfamily,
                stringstyle=\color{red}\ttfamily,
                commentstyle=\color{green}\ttfamily,
                morecomment=[l][\color{magenta}]{\#}
}
\usepackage{mdframed}
\usepackage{multicol}
\usepackage{tcolorbox}
%\usepackage{multirow}
% \usepackage{paralist}
%\usepackage[colorinlistoftodos]{todonotes}
%\usepackage{biblatex}
%usepackage[nolist,nohyperlinks]{acronym}
%\usepackage{amstext}
%\usepackage{hyperref} 
%\usepackage{comment}
%\usepackage{subcaption}
%\renewcommand*{\figureautorefname}{fig.}
%\renewcommand*{\equationautorefname}{eq.}
\usepackage{bm}
\usepackage{comment}
%\usepackage{beamerthemeshadow}
%\usepackage{tikz}
%\usepackage{pgfplots}
%\usepackage{ulem}
%\usepackage[lofdepth,lotdepth]{subfig}
%\newenvironment{figure*}%
%{\begin{figure}}
%{\end{figure}}
%\usepackage[style=mla,babel=hyphen,backend=biber]{biblatex}
% CSE-Beamer-Styles:
\usepackage[course]{beamertheme_sccstalk}
%\usepackage[lecture]{beamertheme_sccstalk}
\usepackage{beamercolorscheme_sccs}
\usepackage{beamerfontthemestructurebold}
\setcounter{tocdepth}{3} 
%colored blocks, example \begin{variableblock}{Title}{bg=blue,fg=white}{bg=white,fg=black}
\newenvironment{variableblock}[4]{%
\setbeamercolor{block title}{#2}
\setbeamercolor{block body}{#3}
\begin{block}{#1}\begin{mdframed}{#4}\end{mdframed}\end{block}}


%some useful commands
%\newcommand{\der}[2]{\frac{\text{d}#1}{\text{d}#2}}
\title{Assignment 4: MPI Collectives and MPI-IO}
\subtitle{Programming of Super Computers}
\author[Friedrich Menhorn, Benjamin R체th, Erik Wannerberg] {Friedrich Menhorn, Benjamin R체th, Erik Wannerberg \\ Team 12} %[displayed in footer]{displayed on title page}
\date{\today}
\institute{Technische Universit채t M체nchen}
\newtheorem*{rem}{Remark}

\usepackage[backend=biber]{biblatex}
\bibliography{References/refs}

\begin{document}
\frame{\maketitle}

\begin{frame}{Contents}
\tableofcontents
\end{frame}


\section{MPI Collectives}
\begin{frame}{\phantom{Contents}}
\tableofcontents[
  currentsection  
]
\end{frame}


\subsection{Optimizations}
\begin{frame}{\insertsubsection}
\begin{itemize}
\item Would you expect performance or scalability benefits from the changes in this application? Explain.
\item Is the resulting code easier to understand and maintain after the changes? If yes, why?
\end{itemize}
\end{frame}


\subsection{Performance Measurements}
\begin{frame}{\insertsubsection}
Show some measurements for falsification/verification of our guess
\end{frame}


\section{MPI Parallel IO}
\begin{frame}{\phantom{Contents}}
\tableofcontents[
  currentsection  
]
\end{frame}


\subsection{Data Sieving and 2-Phase IO}
\begin{frame}{\insertsubsection}
What is "Data Sieving" and "2-Phase IO"? How do they help improve IO performance?
\end{frame}


\subsection{Scalability of original application}
\begin{frame}{\insertsubsection}
\begin{itemize}
\item Was the original implementation scalable in terms of IO performance?
\item Was the original implementation scalable in terms of RAM storage?
\end{itemize}
\end{frame}


\subsection{Impact of parallel IO}
\begin{frame}{\insertsubsection}
How much of the communication in the application was replaced with MPI-IO operations?
\end{frame}
\end{document}
